# Homework Week1

Fantastic unicorns and where to find them.

## Load libs and the csv

```{r}
library(ggplot2)
library(readr)
unicorns <- read_csv("/tmp/unicorn_data.csv")
```

## Plot horn length as a function of weight

Using qplot

```{r}
qplot(unicorns$weight, unicorns$horn.length, geom="line")
```

Add some colour:

```{r}
horn_weight_plot <- ggplot(
  data=unicorns, aes(x=weight, y=horn.length)
  ) + geom_line(colour="red", linetype="dashed", size=1.5)
```

## Model

```{r}
horn_model <- horn_model <- lm(weight ~ horn.length, data = unicorns)
```

Average increase in horn length for one unit of mass [L/M]: `r coef(horn_model)[2]`

### Diagnostic plots

```{r}
qplot(x = fitted(horn_model), y = residuals(horn_model))
qplot(sample = residuals(horn_model))
```

### T-test

Start by separating unicorns by colour

```{r}
pinks <- unicorns[unicorns$colour == 'pink', ]
greens <- unicorns[unicorns$colour == 'green', ]
```

Run as Student's test:

```{r}
t.test(pinks$weight, greens$weight)
```

### Plots

Effect of weight and colour on horn length:

```{r}
qplot(x = weight, colour = colour, y = horn.length, data = unicorns, geom = 'jitter')
```

```{r}
qplot(x = weight, colour = diet, y = horn.length, data = unicorns, geom = 'jitter')
```


Same thing with boxplots:

```{r}
qplot(x = weight, colour = colour, y = horn.length, data = unicorns, geom = 'boxplot')
```

```{r}
qplot(x = weight, colour = diet, y = horn.length, data = unicorns, geom = 'boxplot')
```

## Conclusion

Weight distribution between unicorns of green and pink color is similar, but typically those who eat candy are 20 units heavier, on average, than those who eat flowers. Also, pink unicorns have longer horns than green ones, while diet has no effect on the lengths of their horns.
